\begin{itemize}
  \item Low Voltage Power Supply: Trickle charges the battery when there is mains power and is used in the microcontroller to check if there is mains power available.
  \item Battery: Used to power the microcontroller and all I/O devices.
  \item LM35CZ Temperature Sensor: Sends the current temperature to the microcontroller.
  \item Microcontroller: Receives the data from the LM35CZ sensor and check if the is mains power available. If there is mains power, the microcontroller shall use the normal storage guidelines \cite{bahendekaEADSGGuidelinesInsulin2019}, else the microcontroller shall use the emergency storage guidelines \cite{ManagingInsulinEmergency2021}. The MCU shall also display the current temperature of the insulin or warning messages (on the 3 piece 7 segment). The MCU will also receive a control signal from the reset state button to reset any warning messages on the display.
  \item 3 Piece 7 Segment Display: Will display the current temperature of the insulin detected by the LM35CZ and warning messages such as:
        \begin{itemize}
          \item FZN: If the temperature of the insulin has dropped below $0^{\circ}C$
          \item HOT: If the temperature of the insulin has surpassed $30^{\circ}C$
        \end{itemize}
  \item Reset State Button: Will send a controll signal to the MCU to clear all warnings and check if the is mains power available.
\end{itemize}
The major software functions of this design will be:
\begin{enumerate}
  \item Convert the output of the temperature sensor to temperature in Celsius.
        \item Check if there is mains power available.
        \item If mains power is available, use normal storage guidelines, else use emergency guidelines.
        \item Verify that the temperature meets the guidelines. If it does not meet the guidelines. Raise warning.
        \item Display the current temperature of the temperature sensor. If a warning is raised in the MCU display warning.
        \item If a warning is displayed accept input from button when pressed to clear status and recheck for compliance.
\end{enumerate}
