\chapter{Operation Management System}
The project idea revolves around a micro-controller to be used to determine the arrival of employees, in this case truck drivers, and to let them know which truck they must use in order to pickup the trailers with marchandise to then make their deliveries from the company CPC Logistics. The problem arises due to the fact that the way the truck drivers notify their arival, look for the truck they are supposed to use and find where the trailer is located is done manually. This causes time to be lost, almost 20 minutes while the truck driver searches for the truck they are supposed to use and find the trailer to take to deliver the merchandise. This in turn can produce late delivieres, truck drivers mistaking which trailers they are supposed to take and a lentghy verification of truck drivers if something happens to a truck or trailer. In order to make all this easier and more automated for better efficiency, a micro-controller will be used in combination with an NFC reader and screen to resolve this problem. The NFC reader will make it so the truck driver can identify themselves and be able to get the information they need about the truck they must use, and the screen will help to display this information. Since we would like this micro-controller to be up-to-date with any changed done in the schedule and to make it a compact design that can be used and moved anywhere, a Wi-Fi module would also be beneficial so that the micro-controller can check for the data requested when a truck driver passes their ID card read via NFC, recieve the data from a computer located in another section of the facility and then show the info necessary to the truck driver on the display. In order to power such device, it can be runned from wall power via the use of an adapter, but the addition of a battery can ensure that the system can still function even if there is a power issue at the facility. Also, since if there is a power issue, the micro-controller would not be able to pull new information from a computer. In order to help with this issue, an SD card can be used in order to store this data in case of power failure, that way ensuring that the device can still function and can have the most recent list. 
\newpage
\section{Who is your client? Enrique}
Jose Chompre (Operations Manager at CPC Logistics) 787-514-5895