\section{Cost Analysis}
\subsection{Non-Recurrent Engineering Costs (NRE)}
For this design, we need:

\begin{itemize}
  \item At least 2 MSP-EXP430FR2311 are needed for the creation and debugging of the software for the main and sub units. At \$13.99 per unit from \href{https://www.ti.com/tool/MSP-EXP430FR2311#order-start-development}{Texas Instruments} totaling \$27.98 (not including shipping).
  \item The entire bill of meterials for the main unit \ref{BOM:Main-Unit} totaling $TOTAL$ (not including shipping).
  \item The entire bill of materials for the sub-unit \ref{BOM:Sub-Unit} totaling $TOTAL$ (not including shipping).
  \item At least 2 solderless breadboards at \$2.90 per unit from \href{https://www.digikey.com/en/products/detail/dfrobot/FIT0096/7597069}{Digi-Key}, totaling \$5.80 (not including shipping).
  \item 2 workstation computers for the writing of the software.
  \item At least 150 hours of wages for 3 full time computer engineers spread across:
        \begin{enumerate}
          \item Problem identification
          \item Functional requirements engineering
          \item Functional design engineering
          \item Hardware and software implementation
          \item Testing and Integration
          \item Validation and Deployment
          \item Operation and Maintenance
        \end{enumerate}
At an average salary of \$61.62 per hour \cite{ComputerHardwareEngineers} yields a minimum cost of \$27,729.
This yields a minimum NRE of $TOTAL$.
\end{itemize}
\subsection{Recurring Production Costs (RP)}
Per main unit the cost of parts is $TOTAL$ \ref{BOM:Main-Unit}, assuming there are 50 joints, at \$0.0017 per joint yields a cost per PCB at \$0.085 for PCB assembly. This means that the cost per main unit is $TOTAL$.\\
Per sub unit the cost of parts is $TOTAL$ \ref{BOM:Sub-Unit}, assuming there are 20 joints, at \$0.0017 per joint yields a cost per PCB at \$0.034 for PCB assembly. This means that the cost per main unit is $TOTAL$.\\
