<<<<<<< Updated upstream
\chapter {Potential Project Description Rubén}
The proposal in mind is a micro-processor or micro-controller humidity alert and purifier that uses controllers and sensors to funtion, if the humidity is over a certain amount this is activated or can be disabled by the user or change the detection level preferred by the user. The setting of the problem is which would be designed for almost any household or place that is vulnerable to high humidity that has use by users, this would help in the reporcusions of humidity since high humidity can cause fungus and bacterias to spread or just damage equipment that is vulnerable to high humidity like water damage and respiratory illnesses. This is very common in Puerto Rico thus this system would be very beneficial in health benefits and cost reduction by alerting the user and resolving the problem at the same time manually by an interative system or automated one. 
\newpage
\section{Who is your client? (contact info) Rubén}
Rubén M Melendez (787-447-0633)
\newline
First Bank-Project Coordinator
\newline
Roberto Estrada (787-220-8464)
=======
\documentclass[12pt]{report}
\usepackage{setspace}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\linespread{2.0}
\begin{document}
\section {Humidity and Temperature sensor}

The proporsal in mind is a integrated humidity and temperature sensor that provides high accuracy measurments for humidity levels like the amount of water vapor in the air. The humidity in industrial and home environments is critical to the long-term health and well-being of people or the up keep of the equipment of the insdustry involved. Humidity sensing and control is also important for the safety of equipment and employees. The need that creates the problem is that in theres a high humidity in Puerto Rico since its a tropical island thus this system would be very beneficial in health benefits and cost reduction by alerting the user and resolving the problem at the same time manually by an interative system. The problem adreesed is the humidity problem in warehouses and retail locations that damage documents around the place. The solution scope is the water vapor passes into a conductive electrode that water molecules in the air permeate the humidity sensing dielectric and this changes by the concentration of water and the integrated sensor measures the capatinance and coverts into digital data and also measures the temperature and outputs the information in I2C inter-integrated controller and this runs on a battery bank that also has a USB-C port to do maintenance on the software.  

\newpage
\section {Who is your client? (contact information)}
Rubén M. Melendez (787-447-0633)
\end{document}
>>>>>>> Stashed changes
