\section{Processor Selection}
Based on the global system view, in terms of input output devices (I/O) the sub-unit just requires 1 Bluetooth module and an LED. A cursory glance on the internet reveals that a HC-05 Bluetooth module\cite{InterfacingHC05Bluetooth} uses three I/O and one I/O pin for controlling the LED. The main requires the same two pins for the Bluetooth module and one for detecting power outages. This means that both units need a measly four I/O pins and according to the HC-05 data sheet, the default baud rate is 38400 baud, which translate to 38.4 KHz which most MCUs can easily obtain. There is no intense requirements for computation or memory, but peripherals are required and thus it is justified that an MCU be used for this design. However, the MCU has to be very low power since the sub-units only operate on batteries and have to last at least two years due to the fact that refrigerated vials of insulin can last upwards of a year in ideal conditions. Not only does it need to last 2 years, it needs to take the temperature and keep the current time. With these restrictions in mind, the following three MCUs were chosen as candidates.
\begin{enumerate}
  \item MSP430FR2000: It has 512KB of program memory and 0.5KB of RAM, 12 GPIO pins, 1 UART port, a real-time clock (RTC) and an integrated temperature sensor, running at 16MHz for a price of \$0.276 per unit. It also has a development kit (dev kit) for a price of \$13.99\cite{MSP430FR2000DataSheet}.
  \item MSP430FR2100: It has 1KB of program memory and 0.5KB of ram, 12 GPIO pins, 1 UART port, an RTC and an integrated temperature sensor running at 16MHz for a price of \$0.291 per unit. It shares the same dev kit as the MSP430FR2000\cite{MSP430FR2100DataSheet}.
  \item MSP430FR2110: It has 2KB of program memory and 1KB of ram, 12 GPIO pins, 1 UART port, an RTC and an integrated temperature sensor running at 16MHz for a price of \$0.305 per unit. It shares the same dev kit as the MSP430FR2000\cite{MSP430FR2110DataSheet}.
\end{enumerate}
For the sub-units, at most, they need to hold the current time and 2 bit error data structure in memory, thus the MSP430FR2000 would be an excellent choice for this since they are the lowest cost MCU that meets the feature requirements. For the main unit, the MSP430FR2110 would be great since it could potentially need to hold and process hundreds of error codes at a time, thus the extra ram would be required for this case.
