\begin{enumerate}
  \item Insulin Temperature Warning System
        \begin{itemize}
          \item Feasibility: It is very feasible given 4 month development cycle.
          \item Has it hardware and software opportunities?: It both utilizes the hardware elements within a micro-controller and the flexability and decision making capabilities of a micro-controller to a large extent whilst needing to be low cost.
          \item Dependencies: The delivery of materials from component vendors.
          \item Required technologies: Micro-controller, temperature sensor, memory controller, segment display, rechargeable LIPO batteries, BMS and uninterruptible power supply.
          \item Cost: A rough estimate of the necessary components yielded a cost of \$35.
        \end{itemize}
	\item Operation Management System
	\begin{itemize}
	 \item Feasibility: The design is feasibale at small scale, using limited ID's for testing and few deliveries, but at larger scale would require more testing
          \item Has it hardware and software opportunities?: It has both opportunites due to using NFC cards for use as identification and the need to use Wi-Fi in order to fetch the info needed for the truck driver to fullfil their delivery
          \item Dependencies: The delivery of materials from component vendors, approval of company.
          \item Required technologies: Micro-controller, NFC reader, NFC card, Wi-Fi module, SD card module, battery (with BMS), 7" LCD screen, power delivery (using USB-C)
          \item Cost: The total estimated price of the system is around \$88
	\end{itemize}
        \item Humidity and Temperature sensor
        \begin{itemize}
          \item Feasibility: The feasibility of this design is moderately high, although the design needs special attention to maintainability and upgradability.
          \item Has it hardware and software opportunities?: It utilizes hardware to be able to detect its environment and software to make decisions and notify the user.
          \item Dependencies: The delivery of materials from component vendors.
          \item Required technologies: micro-controller, humidity sensor, battery, BMS, USB-C port, LED display, LED display driver, LED, temperature sensor.
          \item Cost: A rough estimate of the necessary components yielded a cost of \$40.28.
        \end{itemize}
	 \item Cardiac Monitoring Warning System
        \begin{itemize}
          \item Feasibility: A combination of understanding and analyzing heartbeats and using expensive and a poorly documented sensor (i.e heartbeat sensor) makes meeting the project deadline exceedingly difficult.
          \item Has it hardware and software opportunities?: It definitely uses both external sensors and real-time data analysis to justify the need for a micro-controller based design.
          \item Dependencies: The delivery of materials from component vendors.
          \item Required technologies: Micro-controller with a real-time clock, memory controller, small display, battery, BMS, USB port, buzzer, heartbeat sensor.
          \item Cost: A rough estimate of the necessary components yielded a cost of \$28.34.
        \end{itemize}
\end{enumerate}
