\section{System Core Design}
\subsubsection{Integration Order and Verification Plan}
\begin{enumerate}
  \item Connect both MSPEXP-4305438 to the 3.3\si{\V} supply with their respective power supplies.
  \item Connect the LEDs with their respective resistors with the MCU pins and ground.
        \begin{itemize}
         \item To verify that the MSPEXP-4305438 are working, an LED will be lit by a push button in order by the MCU.
        \end{itemize}
  \item Connect the power sense pin to a GPIO of the main unit.
        \begin{itemize}
         \item  To verify that this is working, an LED shall be lit by the MCU when power is absent and off when power is present.
        \end{itemize}
  \item Connect the HM-10 bluetooth modules to the 5\si{\V} supply of their respective power supplies.
  \item Connect the UART pins from the MCU to the HM-10s.
        \begin{itemize}
         \item To verify this, we shall check if it can send a ``Hello World'' to a serial monitor.
        \end{itemize}
  \item Connect the external temperature sensor to the 3.3\si{\V} supply and connect the output pin to a ADC pin on the MCU.
        \begin{itemize}
         \item In order to verify that this is working, we shall use the debugger to see the ADC registers.
        \end{itemize}
\end{enumerate}
\subsubsection{Member Logistic}
\begin{enumerate}
  \item Fabio will complete the ADC integration with thee temperature sensor plus op amp.
  \item Enrique will give the main unit prototype to Fabio.
  \item Fabio will integrate the main and sub units with their respective power supplies.
  \item Fabio will verify that the sub unit can communicate with the main unit.
  \item Enrique will complete the UART integration with the Bluetooth module for the HM-10 for both TXD and RXD interrupts.
  \item Fabio will verify that the host computer can communicate with a host computer.
\end{enumerate}
